Re-finding to support a Deep Web Question Answering System

### 2010-03-05 trunk/paper/semsearch10/content/results_futurework_conclusion.tex
updated text

>>>>

screen_intro.jpg caption:
The user types a natural language query into the search box and clicks submit. The query is then converted into an SSQ and the process of locating appropriate QRMs begins. For any given query there may be several suitable QRMs, these are executed in order of relevance.

screen_results.jpg caption:
After execution has completed, the user is informed of how the query was parsed and what answers were found sorted by relevance. Furthermore, the sequence of pages visited is displayed for the most relevant result.
